Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-08 paper/paper_new.tex

\section{Discussion}
Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, particularly pixel analysis to improve and enrich metadata that enables researchers to apply machine learning to investigate scientific research questions on a scale that has never been pursued before. Our investigation focused on fish in general. Fish are vertebrate animals (phylum Chordata), with current knowledge of there being over 34,000 fish species\cite{fishbase}, and this figure does not include the world of unidentified species. Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype. The ability to analyze thousands of images of of a single fish species computationally can lead to new discoveries that are impossible to manually pursue. Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress \cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity. Efforts to integrate such methods in digital libraries, particularly for digitized specimens, appear to be still somewhat limited, likely due to the diversity of image shapes and sizes. Object detection as explored in our research, working with existing software, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research.

>>>>

\section{Discussion}
Overall our results show a proof of concept and offer a path forward for using object detection technology, enhanced by image informatics techniques, to improve and enrich metadata that enables researchers to pursue advanced specimen image analysis and investigate scientific research questions on a scale that has never been pursued before. Our investigation focused on fish in general. Fish are vertebrate animals (phylum Chordata), with current knowledge of there being over 34,000 fish species\cite{fishbase}, and this figure does not include the world of unidentified species. Species names are merely labels, and the discovery of species variation depends on both genotype and phenotype. The ability to analyze thousands of images of a single fish species computationally can lead to new discoveries that are impossible to manually pursue. Digital library researchers have been concerned with computationally extracting image features, using content based image retrieval methods, and work by Toress \cite{torres2006digital}, while over 15 years old, demonstrates the challenges and opportunity for useful metadata. Efforts to integrate such methods in digital libraries as a means of automatic metadata generation, particularly for digitized specimens, appear to be still somewhat limited, likely due to the diversity of image shapes and sizes. Object detection as explored in our research, working with existing software, is applicable the the larger world of biodiversity, well beyond fish, to include other fauna and flora, art and artefacts, and other digitized images made accessible in for scientific and scholarly research. And following object verification, one can apply pixel analysis to computer XXX
%can we say something here.
